### 2023-10-27 manuscript.tex
update instance seg results [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/a66b2deaac1df041285ed3fcaad6976564efd38f.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/a66b2deaac1df041285ed3fcaad6976564efd38f/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/6668563571

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/489b570261ad55cb98e2b969b432a5ddabce03ae/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/489b570261ad55cb98e2b969b432a5ddabce03ae}{MMV-Lab/im2im-paper@489b570}
on October 27, 2023.

@@

\begin{figure}
\hypertarget{fig:instance}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/embedseg.png}
\caption{(A) Results 2D instance segmentation of \emph{C. elegans}. A minor error can be observed in the zoom-in window. (B) Results of 3D nuclear instance segmentation from fluorescent images and brightfield images. The green box in the fluorescent image highlights a mitotic example. The side view panel shows the segmentation of one specific nucleus along the line annotated in the fluorescent image from the side. The contrast of grayscale images was adjusted using ImageJ's autoscale.}\label{fig:instance}
}
\end{figure}

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/a66b2deaac1df041285ed3fcaad6976564efd38f/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/a66b2deaac1df041285ed3fcaad6976564efd38f}{MMV-Lab/im2im-paper@a66b2de}
on October 27, 2023.

@@

\begin{figure}
\hypertarget{fig:instance}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/instance_seg_justin.png}
\caption{(A) Results 2D instance segmentation of \emph{C. elegans}. A minor error can be observed in the zoom-in window. (B) Results of 3D nuclear instance segmentation from fluorescent images and brightfield images. The green box in the fluorescent image highlights a mitotic example. The side view panel shows the segmentation of one specific nucleus along the line annotated in the fluorescent image from the side. The contrast of grayscale images was adjusted using ImageJ's autoscale.}\label{fig:instance}
}
\end{figure}
